Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-03-28 be.tex
spelling

We assume that the stellar density profile follows a broken power law
with the stellar density $\rhostar\sim r^{-1-\Gamma}= r^{-\delta}$ inside of the
break radius $\rb$, where ($0<\Gamma<1$). We derive an expression for
the specific enthalpy of the gas, $\ke +\gammaf \frac{p}{\rho}$ as a
function of $\zeta=v_w/\sigma$, $x=r/r_s$, and $r_s/\rsoi$. We show
that if the break radius, $\rb$ goes to infinity this quantity
necessarily goes to infinity as the potential well becomes infinitely
deep, hence a break radius is necessary for an outflow to be possible.

>>>>

We derive an expression for the bernoulli parameter of the gas, $\ke
+\gammaf \frac{p}{\rho}+\Phi$, assuming that the stellar density
profile $\rhostar\sim r^{\delta}$ inside of the break radius $\rb$.
